Autonomous Exploration with Exact Inverse Sensor Models

### 2018-06-09 Journal/JINT 2017/JIRS16_rev2.tex
journal added

@@

The trajectory to follow the path outlined by Dijkstra's algorithm is determined with a linear constrained least squares optimization, assuming the robot follows a polynomial trajectory with fixed speed. The starting and ending positions and attitudes may be constrained, and polynomials patched together for long trajectories share a common position and velocity with respect to time. Then, a controller on the robot tracks this trajectory until the robot falls within acceptable thresholds of the final optimal pose. Any control scheme for the motion of the robot can be integrated with the proposed exploration algorithm. Once the robot completes this motion, the entire process is repeated.

%The complete autonomous exploration process is summarized in Table \ref{tab:Alg_AutomousExploration}.

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{experiment_H_per_min.pdf}
	\caption{The map entropy $H$ averaged over all $90601$ grid cells is reduced during experimentation. The quick changes $\Delta H$ per cell correspond to map updates when the robot captures new territory.}
\label{fig:ExperimentH}
\end{figure}

>>>>

This proposed mapping approach follows a Bayesian framework that focusses on occupied and free space, not tracking particular systems or mapping features, such as visual servoing~\cite{ChiDinChe14}. The proposed algorithm may be combined with feature-based approaches for object tracking or stabilization purposes, with the added challenge of associating occupied spaces with features.

@@

The trajectory to follow the path outlined by Dijkstra's algorithm is determined with a linear constrained least squares optimization, assuming the robot follows a polynomial trajectory with fixed speed. The starting and ending positions and attitudes may be constrained, and polynomials patched together for long trajectories share a common position and velocity with respect to time. Then, the robot tracks this trajectory until the robot falls within acceptable thresholds of the final optimal pose. For generality of the proposed exploration algorithm, any position controller yielding robotic motion that follows this desired trajectory may be selected. Once the robot completes this motion, the entire process is repeated.
%The complete autonomous exploration process is summarized in Table \ref{tab:Alg_AutomousExploration}.

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{JIRS_fig11.eps}
	\caption{The map entropy $H$ averaged over all $90601$ grid cells is reduced during experimentation. The quick changes $\Delta H$ per cell correspond to map updates when the robot captures new territory.}
\label{fig:ExperimentH}
\end{figure}
